### 2020-10-18 Analysis/Code/Sorokin_JMP_2020.Rmd
misc

 author: |
  Dmitry Sorokin\thanks{\protect\linespread{1}\protect\selectfont New York University, dsorokin@nyu.edu. I am deeply grateful to Timothy Christensen, Alessandro Lizzeri, and Lu\'{i}s Cabral for their support and guidance. I benefited enormously from my conversations with Ryan Stevens, Jimena Galindo, Sam Kapon, Dmitry Sedov, Jonathan Elliott, and Timur Abbiasov. I would also like to thank Chris Conlon, Christopher Flinn, Elena Manresa, Maher Said, Mikkel Plagborg-M\o{}ller, Milena Almagro, Paula Onuchic, Sharon Traiberman, and all other great people at NYU for their helpful comments. All mistakes are my own.}

>>>>

 author: |
  Dmitry Sorokin\thanks{\protect\linespread{1}\protect\selectfont New York University, dsorokin@nyu.edu. I am deeply grateful to Timothy Christensen, Alessandro Lizzeri, and Lu\'{i}s Cabral for their support and guidance. I benefited enormously from my conversations with Ryan Stevens, Jimena Galindo, Sam Kapon, Dmitry Sedov, Jonathan Elliott, and Timur Abbiasov. I would also like to thank Chris Conlon, Christopher Flinn, Elena Manresa, Maher Said, Mikkel Plagborg-M\o{}ller, Milena Almagro, Paula Onuchic, Sharon Traiberman, Stefan Bucher, and all other great people at NYU for their helpful comments. All mistakes are my own.}
